Behavior-Driven Development in Haskell

### 2012-10-20 paper.tex
behavior driven -> behavior-driven

% These are ignored, unless 'preprint' option specified.
%\titlebanner{A draft paper to be submitted to Haskell Symposium 2012}
\preprintfooter{BDD in Haskell}

\title{Behavior Driven Development in Haskell}
%\subtitle{Subtitle Text, if any}

@@

\subsection{Applying BDD to Haskell: An Example}
\label{sec:bcp-example}
This section shows how behavior driven development works in practice,
by means of the Fibonacci function.  This is a very simple
example, but the method is also applicable to more complicated
situations where design decisions might not be as obvious as here.

@@

\noindent This concludes our example.  We have seen how to utilize
behavior driven development to incrementally build a small library.
We always extend or adapt the specification first, watch it fail,  and
then tighten the implementation.  The combinators {\tt shouldBe}, {\tt
shouldReturn} and {\tt shouldThrow} can be used to specify behavior of
functions in an intuitive, easy to read manner.

>>>>

% These are ignored, unless 'preprint' option specified.
%\titlebanner{A draft paper to be submitted to Haskell Symposium 2012}
\preprintfooter{Behavior-Driven Development in Haskell, a tutorial
introduction}

\title{Behavior-Driven Development in Haskell}
\subtitle{a tutorial introduction}

@@

\subsection{Applying BDD to Haskell: An Example}
\label{sec:bcp-example}
This section shows how behavior-driven development works in practice,
by means of the Fibonacci function.  This is a very simple
example, but the method is also applicable to more complicated
situations where design decisions might not be as obvious as here.

@@

\noindent This concludes our example.  We have seen how to utilize
behavior-driven development to incrementally build a small library.
We always extend or adapt the specification first, watch it fail,  and
then tighten the implementation.  The combinators {\tt shouldBe}, {\tt
shouldReturn} and {\tt shouldThrow} can be used to specify behavior of
functions in an intuitive, easy to read manner.
